Paper

### 2021-12-16 Paper.Rmd
Removed time checker for bootstrap
Added titles to plots

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
    print(i)
  }

@@

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat3[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat4[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

#plot all vaccine curves
ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2]), color='red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green') + 
  labs(x="Day", y="People infected")

>>>>

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
  }

@@

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 Cases Over Time')

@@

ggplot() +
  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat3[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat4[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')

#plot all vaccine curves
ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2]), color='red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green') + 
  labs(x="Day", y="People infected") +
  ggtitle('Covid-19 Cases by Day')
